Outline--Draft JCP format for: Reactive Force Field for Perovskite--Based Solid Oxides and Its Application to Solid Oxide Electrolysis Cells

### 2019-05-17 Paper/paper.tex
Update paper.tex

>>>>

% introduce lanthanum uses
Lanthanum is an element involved either as a catalyst or as a ion in supporting structures of other active catalytic materials.
Particularly, catalysts based on a form of Lanthanum oxide have shown a good efficiency in the oxidative coupling of methane to form ethane and/or ethylene \textbf{import citation}, or as main components of electro--catalysts used in CO$_2$ conversion to CO \textbf{import citation}.

% what is the problem with lanthanum

Given the importance of this element in its applications, quantum mechanical calculations have been carried out to understand its role and influence, if any, on the systems where it is found.
However, many of the phenomena that takes place in catalysis involve the interaction of a
